### 2017-01-04 README.Rmd
add coverage badge to README

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->
[![Travis-CI Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)

>>>>

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->
[![Travis-CI Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/visdat/master.svg)](https://codecov.io/github/njtierney/visdat?branch=master)
